I am writing to apply to the position of Assistant Adjunct Professorship in the Mathematics Department at the University of California, Los Angeles.  I am currently a graduate student at the University of Texas at Austin under the supervision of Andrew Blumberg.  I expect to complete my Ph.D. in May 2021.

My research is in computational equivariant homotopy theory, applied to the modular representation theory of finite groups.  In my thesis work, I used homotopy-theoretic methods to compute the group of endotrivial modules for certain $p$-groups, thereby providing new insights into classical computations and results in modular representation theory.  In future work, I plan to extend my computations to other classes of groups, and I also plan to study other problems in representation theory by constructing and computing novel homotopy invariants. 

I believe that the environment at UCLA would allow my research program to flourish. In particular, my research interests are most closely aligned with those of Professors Mike Hill, Paul Balmer, and Rapha\"el Rouquier.  Furthermore, there is also a strong postdoctoral group, including Christy Hazel and Hood Chatham, as well as the graduate student groups in algebra and topology that I could possibly collaborate with.

Beyond my research program, I would be an active participant and contributor to the department. I have also given various seminar and invited talks, and I have also organized several learning seminars throughout my time at UT Austin.

I am also committed to actively promoting and supporting diversity, inclusivity, and equity in mathematics through both education and outreach.  I would also use my previous experiences to establish new educational or diversity-focused initiatives to support the department.

I have arranged for letters of recommendation to be sent via MathJobs.org from Andrew Blumberg and 
Dan Isaksen, as well as a letter from Mark Daniels,
attesting to my teaching abilities. I am also submitting the AMS cover
sheet, my CV, research statement, teaching statement, and diversity statement. 

I appreciate your time and consideration and look forward to hearing from you.